\bf Measuring background and systemic risk using financial time series

### 2015-06-05 srisk7.tex
pdj changes

Our paper refines and extends the model of \cite{brownlees2015} in several interesting and important ways. First, we reinterpret their SRISK measure as a put on the expected shortfall using stressed expectation. While they condition on the event of a severe market downturn, we take the stressed expectation of the put value. This enables us to capture the impact of increased return volatility due to stress. Second, we decompose their SRISK measure into background stress and imposed system stress. Background stress is a function of existing volatility and leverage. As these factors increase, background stress rises and this makes the firm more susceptible to systemic risk, regardless of the stress event itself. Third,    
\cite{brownlees2015} condition on an absolute cutoff of arbitrary size and length. We suggest that it is also helpful to specify conditional behaviour in percentile terms relative to current market conditions. This provides a sharper focus on the incremental impact of further stress and allows us to draw stronger implications from SRISK numbers. These extensions provide additional insights into the sources and economic nature of systemic risk. They provide potentially new and improved ways of anticipating episodes of heightened systemic risk. Their practical use can be expected to help regulators monitor systemic risk in a timely fashion to facilitate remedial action where necessary.

@@

To illustrate the setup in \eref{bs}, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.    Both panels use the same horizontal and vertical scales.   Thus based on the available data at those two points in  time, policy makers and regulators faced entirely different projections based on the same time series model.   The scatter of dots are the forward simulations.  Note there is no hindsight bias as the model at each time point is based on the available data to that point in time.    The red horizontal line in each panel indicates the Basel limit:  any firm return less than the limit would constitute a Basel breach.   In the left panel there is little confidence that the Basel limit will be reached since it requires a return on equity approaching 20\% -- with confidence less than xxx the Basel standard will be breached.  In the right panel there is no chance of a Basel breach under any of the projected return on equity view -- the bank is ``safe."

>>>>

Our paper refines and extends the model of \cite{brownlees2015} in several  ways. First, we reinterpret their SRISK measure as a put on the expected shortfall using stressed expectation. While they condition on the event of a severe market downturn, we take the stressed expectation of the put value. This enables us to capture the impact of increased return volatility due to stress. Second, we decompose their SRISK measure into background stress and imposed system stress. Background stress is a function of existing volatility and leverage. As these factors increase, background stress rises and this makes the firm more susceptible to systemic risk, regardless of the stress event itself. Third,    
\cite{brownlees2015} condition on an absolute cutoff of arbitrary size and length. We suggest that it is also helpful to specify conditional behaviour in percentile terms relative to current market conditions. This provides a sharper focus on the incremental impact of further stress and allows us to draw stronger implications from SRISK numbers. These extensions provide additional insights into the sources and economic nature of systemic risk. They provide potentially new and improved ways of anticipating episodes of heightened systemic risk. Their practical use can be expected to help regulators monitor systemic risk in a timely fashion to facilitate remedial action where necessary.

@@

To illustrate the setup in \eref{bs}, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.    Both panels use the same horizontal and vertical scales.   Thus based on the available data at those two points in  time, policy makers and regulators faced entirely different projections based on the same time series model.   The scatter of dots are the forward simulations.  Note there is no hindsight bias as the model at each time point is based on the available data to that point in time.    The red horizontal line in each panel indicates the Basel limit:  any firm return less than the limit would constitute a Basel breach.   In the left panel there is little confidence that the Basel limit will be reached since it requires a return on equity approaching 20\%.  In the right panel there is no chance of a Basel breach under any of the projected return on equity view -- the bank is ``safe."
